\vspace{-2cm} Inference on the Effects of Observed Features \\ in Latent Space Models for Networks

### 2016-04-14 manuscript.tex
remove se in graphs, up mc iter, reduce param for beta.var

We first compute the MLE estimated by iteratively reweighted least squares in \texttt{R}. For the LSM we use the posterior mode. In the cases where edges are Binomial or Poisson distributed, we scale the estiamtes % figure out how to do this.

>>>>

We first compute the MLE estimated by iteratively reweighted least squares in \texttt{R}. For the LSM we use the posterior mode. In the cases where edges are Binomial distributed, we scale the estiamtes using the reciprocal of the bias of $\beta_1$ when $X$ and $d$ are independent: $\frac{\sqrt{3.28 + \beta_2^2 \text{Var(d)}}}{\sqrt{3.29}}$, where $3.29$ is the variance of a standard logistic distribution \cite{mood2010logistic}.
